A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-02-23 manuscript.tex
:construction: extraction results transition

% ref labels
\newcommand{\fgrref}[2][]{\hyperref[#2]{Figure \ref*{#2}#1}}
\newcommand{\tblref}[2][]{\hyperref[#2]{Table \ref*{#2}#1}}
\newcommand{\appref}[2][]{\hyperref[#2]{Appendix \ref*{#2}#1}}

@@

Thus, while the final selection of features should always be driven by the research questions and field-specific conventions, for our illustration we chose six features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. An overview of the selected features, their substantive interpretations, and mathematical operationalizations is also available in \tblref{tab:esmFeatures}. We offer a short introduction of each of these six features below as a practical starting point for researchers and practitioners interested in feature-based clustering of psychological time series data. We provide additional background on the theoretical relevance of the selected features in \appref{app:FeatureBackground}.

>>>>

% ref labels
\newcommand{\fgrref}[2][]{\hyperref[#2]{Figure \ref*{#2}#1}}
\newcommand{\tblref}[2][]{\hyperref[#2]{Table \ref*{#2}#1}}
\newcommand{\appref}[2][]{\hyperref[#2]{Appendix \ref*{#2}#1}}
\newcommand{\equatref}[2][]{\hyperref[#2]{Equation \ref*{#2}#1}}

@@

Thus, while the final selection of features should always be driven by the research questions and field-specific conventions, for our illustration we chose six features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. An overview of the selected features, their substantive interpretations, and mathematical operationalizations is also available in \tblref{tab:esmFeatures}. We provide additional background on the theoretical relevance of the selected features in \appref{app:FeatureBackground}. For each of the six time series features we chose, we chose a mathematical representation that was appropriate for our type of data. We provide a short introduction of each feature below.
